Example and Tutorial for Vim Editor (Linux)

### 2020-01-07 nontex/install/linux/fn_vim.Rmd
installation atom keymap, yiw and viwp

"""""""""""""""""""""""""""""""""""""""""""""""""
" UI Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" Keep cursor in the middle of the page, useful for editing text
set so=999
" Turn limelight on by default
" autocmd VimEnter * Limelight
" Turn Goyo on by default
autocmd VimEnter * Goyo
" autocmd VimEnter * AirlineToggle
" In Goyo, if airline is turned on, do nto show scratch area
" autocmd! User GoyoEnter nested set eventignore=FocusGained
" autocmd! User GoyoLeave nested set eventignore=
```

@@

"""""""""""""""""""""""""""""""""""""""""""""""""
" Other Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
set paste               " to enable pasting in windows
```

@@

1. Delete:
    - delete current word and go into insert mode: *ciw*
    - Delete current word: *dw*
    - Delete from cursor until end of sentence: *dis*
    - Delete from cursor to end of line: *d$* or *D*
    - Delete until end of paragraph: *dip*
    - Delete all text in file: *ggdG*

>>>>

"""""""""""""""""""""""""""""""""""""""""""""""""
" UI Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" Keep cursor in the middle of the page, useful for editing text
set so=999
" Turn limelight on by default
" autocmd VimEnter * Limelight
" Turn Goyo on by default
autocmd VimEnter * Goyo
" autocmd VimEnter * AirlineToggle
" In Goyo, if airline is turned on, do nto show scratch area
" autocmd! User GoyoEnter nested set eventignore=FocusGained
" autocmd! User GoyoLeave nested set eventignore=
""""""""""""""""""""""""""""""""""""""""""""""""""
" Remap Keys
"""""""""""""""""""""""""""""""""""""""""""""""""
" esc in insert mode
" inoremap jj <esc>
```

@@

"""""""""""""""""""""""""""""""""""""""""""""""""
" Other Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
set paste               " to enable pasting in windows
set nofoldenable        " avoid folding by default

"""""""""""""""""""""""""""""""""""""""""""""""""
" Remap Keys
"""""""""""""""""""""""""""""""""""""""""""""""""
" esc in insert mode
" inoremap jj <esc>
```

@@

**Delete**:

- delete current word and go into insert mode: *ciw*
- Delete current word: *dw*
- Delete from cursor until end of sentence: *dis*
- Delete from cursor to end of line: *d$* or *D*
- Delete until end of paragraph: *dip*
- Delete all text in file: *ggdG*

**Copying**: replace *d* by *y* for all oeprations.

- Copy current word: *dw*
- Copy from cursor to end of line (need to set this): *y$* or *Y*
- Copy until end of paragraph: *yip*

**Insert to edit**:

- Insert after last character of document: *GA*
- Insert at the end of line: *A*
- Insert after cursor, *a*, insert before curosr *i*

**Copy and Replace**:

- copy current word: *yiw*, then move to the next word to replace: *viwp*
